\include{settings}
\include{commands}
\include{contact}

\begin{document}
    \fontfamily{ppl} \selectfont

    \begin{resheader}{\name}{\email}{\addr}{\phone}
        Blah, blah, blah, this is the lead-in paragraph where I talk
        about how awesome I am in one or two sentences. It's proving
        difficult to write.
    \end{resheader}

    \ressection{Qualifications}

    \begin{reslist}
        \item{Capable of conversing functionally with business users and
              technically with colleagues as well as translating
              requirements between the two.}
        \item{Comfortable in an environment where high scalability and
              availability are key requirements of the application
              being developed.}
        \item{Curious and self-motivated; develops outside of work,
              authoring and contributing to a number of open source
              software projects.}
        \item{Extremely comfortable in Unix-based systems and working
              via the shell.}
    \end{reslist}

    \ressection{Technical Expertise}

    \begin{restable}
        {\bf Languages}:    & Ruby, Haskell, JavaScript, C, C\#, X++,
                              PHP, Perl, Python, HTML/CSS, Shell \\
        {\bf Frameworks}:   & Rails, Yesod, Prototype, Underscore, Node,
                              .NET, TestUnit, RSpec \\
        {\bf Technologies}: & Postgresql, MySQL, MongoDB, MSSQL, Riak,
                              Nginx, Unicorn, Apache, Amazon Web
                              Services, Graphite, Chef, Capistrano
    \end{restable}

    \ressection{Professional Experience}

    \resitem{Ideeli Inc}{New York, NY}{Software Engineer}{2011 - present}

    Work both independently and as part of an Agile development team to
    design and implement critical fixes and enhancements to a large
    legacy Ruby on Rails Application. Use Test Driven Development and
    performance benchmarking to ensure the application continues to
    serve its 5 million users effectively.

    \begin{reslist}
        \item{Chosen as a key Developer in an application-wide
              re-architecting to be entirely service-based.}
        \item{Independently developed a Skype bot to notify us of build
              failures, automate deployments and provide in-chat access
              to documentation and ticket tracking systems.}
    \end{reslist}

    \resitem{Green Beacon Solutions LLC}{Newton, MA}{ERP Consultant}{2008 - 2011}

    Interfaced with clients to gather business requirements and create
    functional specifications for custom solutions. Developed both
    front-end user interfaces and back-end algorithms in X++, C\# and
    Transact-SQL to meet the defined business needs.

    \begin{reslist}
        \item{Developed custom .NET client for Dynamics AX used on
              hand-held devices.}
        \item{Received advanced certifications in both functional and
              technical areas of MS Dynamics AX.}
    \end{reslist}

    \resitem{Cooper Industries}{Chelsea, MA}{Manufacturing Engineer}{2007 - 2008}

    Authored build-to-print process instructions for the manufacture of
    custom cable assemblies. Introduced Lean principles into the
    manufacturing and QA processes. Ensured site compliance with Cooper
    Industries comprehensive environmental and safety regulations.

    \begin{reslist}
        \item{Acted as Department lead during the transition to SAP
              defining requirements and providing training and
              documentation back to the team.}
    \end{reslist}

    \ressection{Education}

    \resitem{Boston University}{Boston, MA}{Bachelor of Science, Aerospace Engineering}{5/07}
\end{document}
